---
title: "$5 Dollar Game Analysis"
output: 
  html_document:
    theme: yeti
---

------------------------------------------------------------------------

```{r include = FALSE}

source("data_prep.R")
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.align = "center")

x5 <- 4
```

#### Winning Tickets Claimed vs \# Tickets in Game/Age of Game {style="text-align: center"}

```{r}
tickets_age_per_claimed_plot[[x5]]
```

::: {style="text-align: center"}
Most favorable games are located in the lower left quadrant in the red box. This typically would mean an older game with a lower number of tickets available and a low % of winning tickets claimed
:::

------------------------------------------------------------------------

#### Odds of \>\$500 Winning Ticket vs \# of Tickets in Game {style="text-align: center"}

```{r}
odds_500_tickets_plot[[x5]]
```

::: {style="text-align: center"}
Games located in the red box have the highest odds of picking a \>\$500 Winning Scratch-Off and have the fewest number of tickets in the game. Avoid games outside the red box for the best chance of winning.
:::

------------------------------------------------------------------------

#### % of Winning Tickets Claimed vs Age of Game {style="text-align: center"}

```{r}

per_claim_plot_list[[x5]]
```

::: {style="text-align: center"}
Use this plot to track your favorite game over time. For the best chance of winning target games that have % of winning tickets claimed well below the blue trend line. An older game with low % winners claimed can provide good opportunity. Newer games have more unknowns but more chances at big winners.
:::
